Emulsions Stabilized by Magnetic Ellipsoidal Particles: A Lattice Boltzmann Study

### 2025-04-07 chapters/paper2.tex
Changes 1. Modified conclusion section in final remarks 2. Changes image sized in structural response of bijels 3. modified abstract and introduction to include structural analysis results

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
         row detail the microstructure evolution for bijels with no applied field while the bottom rows show bijels stabilized by oblate and prolate particles 
         respectively with a field strength of $\bar{B} = 1$ applied.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_on.png} 
\caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
         \(S\) (lines) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying 
         magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
\label{fig:domain_size-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
         both in the absence of a magnetic field (top row) and with a magnetic field applied (\(\bar{B}_z = 1\), bottom row). Particle reorientation to the
         applied field can be observed.} 
\label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/psi-field_on.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) over time for bijels stabilized 
             by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The response of \(\langle \psi \rangle\) 
             differs notably between the two particle morphologies.} 
    \label{fig:interface_angle-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/Q6-field_on.png} 
    \caption{Plots of the time evolution of the six-fold Steinhardt bond order parameter \(\langle Q_6 \rangle\) for bijels 
             stabilized by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The dynamics of interfacial ordering differ 
             significantly between particle morphologies with \(\langle Q_6 \rangle\) decreasing over time for oblate particles and increasing for prolate particles.} 
    \label{fig:interface_angle-field_on} 
\end{figure}

From Figure \ref{fig:interface_angle-field_on} the time evolution of \(\langle Q_6 \rangle\) can be qualitatively divided into three regimes;
an initial transition period, a plateau, and a final reordering or jamming phase.
For oblate particles, application of the magnetic field initially causes a sharp decrease in \(\langle Q_6 \rangle\), reflecting a disruption of the 
pre-existing interfacial order as particles begin to tilt and rearrange. This is followed by a plateau, during which ordering is temporarily suppressed 
as particles continue reorienting. Finally, \(\langle Q_6 \rangle\) begins to increase gradually, indicating partial recovery of local order as the system 
evolves toward a new jammed state. The rate of change of \(\langle Q_6 \rangle\) significantly decreases toward the end of the simulation, suggesting the onset 
of kinetic arrest. The final value of \(\langle Q_6 \rangle\) is dependent on the applied magnetic field strength, with higher field strengths 
resulting in lower final ordering, potentially due to increased variance in the interfacial angle, reducing packing efficiency.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.5]{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
             stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
             particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
             perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
             demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes—quantified by domain size—diminish 
with each successive increase in magnetic field strength. This saturation behavior suggests a direct link between the extent of domain coarsening 
and the evolving order within the interfacial particle monolayer. As demonstrated in the previous section, once the bijel is jammed, further domain 
growth is constrained by local rearrangements of the particles at the interface, which are themselves influenced by the degree of particle alignment 
and packing. To investigate this relationship further, we now examine how pre-existing particle order, established during bijel formation, affects 
the system's responsiveness to a subsequent applied magnetic field.

@@

\begin{figure}
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/microstructure_viz-field_up.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial (left column) and final (right column)
         timepoints for two magnetic field conditions. The top row corresponds to the case where the field is increased from 
         \(\bar{B}_z = 0.2\) to \(\bar{B}_z = 1.0\), while the bottom row shows a bijel formed and evolved under a constant field of 
         \(\bar{B}_z = 1.0\). }
\label{fig:microstructure_viz-field_up}
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_up.png} 
\caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
         We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
\label{fig:domain_size-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_up.png} 
\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
         oblate and prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field 
         strength, $\Delta B$. The anisotropic domain size is inversely correlated to the tortuosity and $L_{perp}$ changes for 
         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
\label{fig:domain_size_aniso-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.2]{../figures/results/paper2/particle_viz-field_up.png} 
\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
\label{fig:particle_viz-field_up} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper2/psi-field_up.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) for bijels stabilized 
             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
             The dynamics observed can be seen to be a function of the initial microstructure.} 
    \label{fig:interface_angle-field_up} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper2/Q6-field_up.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle Q6 \rangle\) for bijels stabilized 
             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
             The dynamics observed can be seen to be a function of the initial microstructure.} 
    \label{fig:Q6-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/domain_size-field_down.png} 
\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
         is switched off, along with a reduction in the ordering of the particles.} 
\label{fig:domain_size-field_down} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale = 0.5]{../figures/results/paper2/domain_size_aniso-field_down.png} 
\caption{Plots of the anisotropic structural response of bijels after the removal of 
         magnetic fields, by showing the relative change in directional domain size \((\Delta L)\) and tortuosity \((\Delta \tau)\) 
         as a function of \(\Delta \bar{B}\), the change in field strength from the templated to final state. Blue curves correspond 
         to bijels stabilized by oblate particles, and red curves to those stabilized by prolate particles.} 
\label{fig:domain_size_aniso-field_down} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/interface_angle-nint-field_down.png} 
\caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
         on the left and right plots respectively. They show slight increases in $\langle \psi \rangle$ over time indicating that the particles are
         slowly tilting out of the interface, inducing the domain coarsening observed.} 
\label{fig:interface_angle-field_down} 
\end{figure}

@@

In this chapter, we investigated the microstructural response of bijels stabilized by anisotropic magnetic ellipsoids under varying magnetic field protocols. 
By systematically analyzing the evolution of domain size, anisotropy, and particle-level order in response to increasing and decreasing magnetic fields, 
we uncovered key mechanisms that govern structural adaptability and kinetic stability in these systems.

We first demonstrated that bijels subjected to increasing magnetic field strength exhibit hysteresis in its structural response, wherein the domain size increases 
with field application but does not revert upon field removal. This behavior was attributed to particle reorientation at the interface, which induces local 
unjamming and subsequent domain coarsening. Through visualization and quantitative analysis, we showed that reorientation causes particles to tilt out of the 
interface, reducing the stabilized interfacial area and driving fluid domain coalescence. Importantly, this microstructure change is constrained by the degree 
of initial particle disorder with systems containing pre-aligned particles exhibiting diminished structural response, indicating that reorientation, not field strength 
alone is the primary driver of field-induced structural response.

Two distinct categories of structural response emerged: one in which disordered particle monolayers undergo magnetic reordering that enables large-scale domain 
coarsening, and a second in which initially ordered systems reorient locally but remain globally jammed, leading to minimal structural adaptation. This transition 
was further reinforced by the observed saturation in domain growth as a function of particle alignment, highlighting a limit to how much structural change can be 
achieved post-jamming.

Upon magnetic field removal, we found that the bijel microstructure remains largely unchanged, consistent with the kinetic arrest characteristic of these systems. 
While the particle monolayer exhibited gradual relaxation—evident through changes in interface angle—these dynamics were insufficient to trigger significant domain 
restructuring. Directional domain size and tortuosity metrics further confirmed that coarsening post field removal was isotropic and minimal, regardless of initial 
ordering.

Collectively, these results elucidate the role of particle-level interactions in dictating the field-responsive behavior of bijels. They reveal that while 
magnetic fields offer a route to tailor microstructure on demand, the efficacy of this control hinges on the degree of initial disorder and the system’s 
jamming history. This mechanistic understanding provides design principles for harnessing bijel responsiveness in practical applications—such as tunable 
porous media, controlled release scaffolds, or adaptive separation systems—where reversibility, anisotropy, and stability must be precisely managed.

% Owing to the applicability of bijels in the catalyst support, filtration membrane and drug release spaces, we were interested in identifying how bijels stabilized 
% by magnetically responsive ellipsoidal particles could be used to create active soft matter. In this work, we have studied the effect of the application, increase 
% or removal of magnetic fields on the structural response of bijels stabilized by magnetically responsive ellipsoids using hybrid Lattice Boltzmann-Molecular Dynamics 
% simulations. We first characterized the hysteresis curve of the bijel, identifying that the process history dependence of the bijel microstructure. To identify why 
% We observed the path dependence and the microstructure change observed when applying magnetic fields after synthesis, we considered three starting setups; The first 
% applying a field of varying strength to bijel templates that were simulated with no magnetic field applied. The second involved increasing the applied field 
% strength onto bijel templates that were simulated with increasing field strengths. The final setup involves removing a field from bijel templates that were simulated 
% with various field strengths.

% We found that application of magnetic fields onto bijels stabilized by magnetically responsive ellipsoidal particles results in an average microstructure change up to 
% $5\%$ when investigating changes in the average microstructure. We also identified that the structures become anisotropic upon application of the magnetic field for 
% oblate and prolate particles. The anisotropy is particle dependent with bijels stabilized by oblate particles seeing an increase in $L_{\perp}$ of up to $60\%$ and for 
% prolate particles an increase in $L_{\parallel}$ of up to $40\%$ with a corresponding decrease in the tortuosity in that axis. This is caused by the reorientation of the 
% particles to the magnetic field, followed by domain coarsening as the interfacial coverage of the particles decrease, before jamming in place again. We characterize that 
% while particle reorientation to the applied field initiates microstructural response, local rearrangement of the particle monolayer is the controlling mechanism of 
% domain size evolution as characterized by identifying the dominant timescales 
% of response for both particle morphologies. However, their time evolution is different with bijels stabilized by prolate particles undergoing a local crystallization when 
% the average six fold Steinhardt order parameter or $\langle Q_6 \rangle \geq 0.38$. For bijels stabilized by oblate particles, a global minimum of the $\langle Q_6 \rangle$ 
% characterizes the dynamics of the system.

% When increasing the applied field strength, we observe that the difference between the final and initial magnetic fields is correlated to the domain size change observed. 
% We observe that the anisotropic domain size changes are also dependent upon this difference, with the largest difference being observed when characterizing a bijel template 
% simulated under no field before having a field strength of $\bar{B} = 1$ applied to it. When looking at the particle monolayer, we characterize three behaviors seen from the 
% average interfacial angle $\langle \psi \rangle$ and $\langle Q_6 \rangle$. These behaviors are further differentiated for each particle morphology. For oblate particles, 
% the first behavior is characterized as a reorientation of the particle on the interface seen as an increase in $\langle \psi \rangle$ over time with a corresponding decrease 
% in $\langle Q_6 \rangle$ as the particles do not close pack anymore. For prolate particles, we see a slight reduction in $\langle \psi \rangle$ and greater ordering of the 
% particles from $\langle Q_6 \rangle$. The second behavior originates from small reorientations of the particles at the monolayer which do not greatly affect the interfacial 
% angle but cause a loss or gain of particle order on the interface. The final behavior is characterized as long timescale domain coarsening as there is no change between the 
% applied magnetic field and the magnetic field used to simulate the template.

% Finally, when decreasing the magnetic field strength, we observe little difference between bijel templates made with any field strength and no field. From the average domain 
% size, we see that the bijels coarsen at approximately the same rate. Upon further investigation of the microstructure anisotropy, we identify that the anisotropic structure 
% does not change as well, suggesting coarsening effects are independent of the effect of the local differences at the particle monolayer. After characterizing 
% $\langle \psi \rangle$ and $\langle Q_6 \rangle$, we see differences at the initial state which, while changing the initiation point of the dynamics, does not play a large
%  role otherwise. Thus any domain size change observed when removing a field is due to interfacial capillary interactions.

% It has been shown how the domain size and tortuosity can be used to adjust the flow rate, separations efficiency or reaction rate in applications such as cross-flow reactors, 
% drug delivery and liquid-liquid extraction. These results show that the properties of bijels can be tuned in-situ for these applications although it appears that it can only 
% be done once. With the results presented here, we have considered only one set of parameters that control the dynamics. Parameters not changed such as the fluid density, 
% viscosity, surface tension and volume fraction of particles may impact the mechanisms and rate of domain size control. We also do not consider magnetic 
% fields applied in different directions which even in this simple setup may be able to modify the microstructure considerably, or gradient magnetic fields which may allow 
% more effective unjamming and re-jamming dynamics for further microstructure modification than what has been shown here.

% Effects such as the steric hindrance between particles may lessen as particle size reduces as particles are more easily able to conform to the curvature of the interface. 
% The impact this may have on the results seen with the micron-sized particles used here is unknown. In many of the applications listed above, it is also unknown how changes 
% in the spacing between particles affect underlying reactivity, selectivity or diffusion rates which have implications past the domain size and tortuosity changes characterized 
% in the literature. Furthermore, it is unknown how additional particle interactions such as chemical cross-linking or charge affect the results seen here. Both strategies are 
% used in bijels to reinforce them against shear to facilitate higher shear rates, useful in cross-flow reactors and separation membranes. In conclusion, our simulations provide 
% qualitative trends into the expected microstructure change and their underlying mechanisms and timescales when applying or removing a field from a bijel stabilized by 
% anisotropic particles by modifying their orientation and packing.

>>>>

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate particles simulated under no fields at $t = 0$ (left columns) and $t = 10^5$ (right columns). The top 
         row detail the microstructure evolution for bijels with no applied field while the bottom rows show bijels stabilized by oblate and prolate particles 
         respectively with a field strength of $\bar{B} = 1$ applied.}
\label{fig:microstructure_viz-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_on.png} 
\caption{Plots of the time evolution of the normalized domain size \(L/R\) (markers) and nematic order parameter 
         \(S\) (lines) for bijels stabilized by oblate (left, \(\alpha = 0.5\)) and prolate (right, \(\alpha = 2.0\)) ellipsoidal particles under varying 
         magnetic field strengths. Here, \(R = 7.9\) is the volume-equivalent sphere radius.} 
\label{fig:domain_size-field_on} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.5]{../figures/results/paper2/particle_viz-field_on.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial and final timesteps, 
         both in the absence of a magnetic field (top row) and with a magnetic field applied (\(\bar{B}_z = 1\), bottom row). Particle reorientation to the
         applied field can be observed.} 
\label{fig:particle_viz-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/psi-field_on.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) over time for bijels stabilized 
             by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The response of \(\langle \psi \rangle\) 
             differs notably between the two particle morphologies.} 
    \label{fig:interface_angle-field_on} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/Q6-field_on.png} 
    \caption{Plots of the time evolution of the six-fold Steinhardt bond order parameter \(\langle Q_6 \rangle\) for bijels 
             stabilized by oblate (left) and prolate (right) ellipsoidal particles under varying magnetic field strengths. The dynamics of interfacial ordering differ 
             significantly between particle morphologies with \(\langle Q_6 \rangle\) decreasing over time for oblate particles and increasing for prolate particles.} 
    \label{fig:Q6-field_on} 
\end{figure}

From Figure \ref{fig:Q6-field_on} the time evolution of \(\langle Q_6 \rangle\) can be qualitatively divided into three regimes;
an initial transition period, a plateau, and a final reordering or jamming phase.
For oblate particles, application of the magnetic field initially causes a sharp decrease in \(\langle Q_6 \rangle\), reflecting a disruption of the 
pre-existing interfacial order as particles begin to tilt and rearrange. This is followed by a plateau, during which ordering is temporarily suppressed 
as particles continue reorienting. Finally, \(\langle Q_6 \rangle\) begins to increase gradually, indicating partial recovery of local order as the system 
evolves toward a new jammed state. The rate of change of \(\langle Q_6 \rangle\) significantly decreases toward the end of the simulation, suggesting the onset 
of kinetic arrest. The final value of \(\langle Q_6 \rangle\) is dependent on the applied magnetic field strength, with higher field strengths 
resulting in lower final ordering, potentially due to increased variance in the interfacial angle, reducing packing efficiency.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/domain_size_aniso-field_on.png} 
    \caption{Plotting the anisotropic domain size and tortuosities against the applied magnetic field strength on the left and right respectively for bijels 
             stabilized with magnetically responsive oblate and prolate ellipsoids. We see that upon application of the field, bijels stabilized with prolate 
             particles experience a domains ize increase in the direction parallel to the applied field direction, $L_{\parallel}$, while the domain size 
             perpendicular to the applied field, $L_{\perp}$ decreases. The opposite is true for bijels stabilized with oblate particles. The tortuosity data 
             demonstrate that as the domain size increases, the tortuosity decreases and vice versa.} 
    \label{fig:domain_size_aniso-field_on} 
\end{figure}

@@

The hysteresis curve presented earlier in Figure~\ref{fig:hysteresis_curve} revealed that microstructural changes diminish 
with each successive increase in magnetic field strength. This saturation behavior suggests a direct link between the extent of domain coarsening 
and the evolving order within the interfacial particle monolayer. As demonstrated in the previous section, once the bijel is jammed, further domain 
growth is constrained by local rearrangements of the particles at the interface, which are themselves influenced by the degree of particle alignment 
and packing. To investigate this relationship further, we now examine how pre-existing particle order, established during bijel formation, affects 
the system's responsiveness to a subsequent applied magnetic field.

@@

\begin{figure}
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/microstructure_viz-field_up.png} 
\caption{Visualizations of bijels stabilized by prolate ellipsoidal particles at the initial (left column) and final (right column)
         timepoints for two magnetic field conditions. The top row corresponds to the case where the field is increased from 
         \(\bar{B}_z = 0.2\) to \(\bar{B}_z = 1.0\), while the bottom row shows a bijel formed and evolved under a constant field of 
         \(\bar{B}_z = 1.0\). }
\label{fig:microstructure_viz-field_up}
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_up.png} 
\caption{Plot of the spherically averaged domain size normalized with $Rp(L/R)$ of the particle in markers and the nematic order parameter in lines. 
         We show that the domain size change measured is correlated to the change in the particle ordering, characterized using the nematic order parameter.} 
\label{fig:domain_size-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_up.png} 
\caption{Plotting the anisotropic domain sizes and tortuosity at the final timestep on the left and right respectively for bijels stabilized with 
         oblate and prolate ellipsoidal particles starting at different particle orders. We plot these results against the change in the applied field 
         strength, $\Delta B$. The anisotropic domain size is inversely correlated to the tortuosity and $L_{perp}$ changes for 
         a bijel made with $\bar{B} = 1 \rightarrow 1$ and $\bar{B}: 0 \rightarrow 1$ differ, suggesting that the processing history of the bijel is important.} 
\label{fig:domain_size_aniso-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.4]{../figures/results/paper2/particle_viz-field_up.png} 
\caption{Snapshots of the structural evolution of the particle monolayer in bijels stabilized by prolate ellipsoids 
         under different magnetic field conditions. The top row corresponds to a simulation where the field is increased from 
         \(\bar{B} = 0.2\) to \(\bar{B} = 1.0\), while the bottom row shows a system maintained at a constant field of \(\bar{B} = 1.0\) throughout.} 
\label{fig:particle_viz-field_up} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/psi-field_up.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle \psi \rangle\) for bijels stabilized 
             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
             The dynamics observed can be seen to be a function of the initial microstructure.} 
    \label{fig:interface_angle-field_up} 
\end{figure}

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.6]{../figures/results/paper2/Q6-field_up.png} 
    \caption{Plots of the evolution of the average interface angle \(\langle Q6 \rangle\) for bijels stabilized 
             by oblate (left) and prolate (right) particles, as a function of the initial microstructure and subsequent magnetic field application.
             The dynamics observed can be seen to be a function of the initial microstructure.} 
    \label{fig:Q6-field_up} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/domain_size-field_down.png} 
\caption{Plot of the spherically averaged domain size normalized with $R_p$ of the particle and the nematic order parameter of each bijel over time. 
         Each color represents bijel templates made with different field strengths $\bar{B}$. We show that there is domain coarsening when the field 
         is switched off, along with a reduction in the ordering of the particles.} 
\label{fig:domain_size-field_down} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale = 0.6]{../figures/results/paper2/domain_size_aniso-field_down.png} 
\caption{Plots of the anisotropic structural response of bijels after the removal of 
         magnetic fields, by showing the relative change in directional domain size \((\Delta L)\) and tortuosity \((\Delta \tau)\) 
         as a function of \(\Delta \bar{B}\), the change in field strength from the templated to final state. Blue curves correspond 
         to bijels stabilized by oblate particles, and red curves to those stabilized by prolate particles.} 
\label{fig:domain_size_aniso-field_down} 
\end{figure}

@@

\begin{figure} 
\centering 
\includegraphics[scale=0.6]{../figures/results/paper2/psi-field_down.png} 
\caption{Plots of the average interfacial angle $\langle \psi \rangle$  plotted against time for bijels stabilized by oblate and prolate particles
         on the left and right plots respectively. They show slight increases in $\langle \psi \rangle$ over time indicating that the particles are
         slowly tilting out of the interface, inducing the domain coarsening observed.} 
\label{fig:interface_angle-field_down} 
\end{figure}

@@

In this work, we investigated how magnetic fields influence the structure and dynamics of bijels stabilized by magnetically responsive ellipsoidal particles. Motivated 
by the relevance of bijels in applications such as catalysis, membrane filtration, and drug delivery, we explored how external stimuli can enable in-situ control over 
microstructure in these systems. Using hybrid Lattice Boltzmann-Molecular Dynamics simulations, we characterized the structural response of formed bijels by investigating
the effect of applying a magnetic field and the initial microstructure on the structural response characterized. We first demonstrated that bijels subjected to increasing 
magnetic field strength exhibit hysteresis in its structural response, where the domain size increases with field application but does not revert upon field removal.

When investigating the effect of the application of magnetic fields, our results revealed that applying magnetic fields post-formation induces domain coarsening up to 5\%, with 
field-induced anisotropy dependent on particle shape. Oblate particles exhibited growth primarily in the perpendicular direction by up to 60\%, while prolate particles showed coarsening 
along the field direction up to 40\%, 
both accompanied by a decrease in tortuosity. These changes arise from particle reorientation to the field, followed by local unjamming and interfacial rearrangement before 
re-jamming occurs, as characterized using the average interface angle of the particles and the Steinhardt bond orientational order parameter.

Importantly, the extent of microstructural change scales with the difference in magnetic field strength before and after application. We found that particle alignment 
characterized via $\langle \psi \rangle$ and $\langle Q_6 \rangle$ governs domain evolution. Disordered particle layers exhibited strong field responses, while highly ordered 
templates showed minimal change, highlighting the importance of reordering on the structural response observed. In contrast, removing the magnetic field had little effect 
on bijel structure. Domain size and anisotropy remained largely unchanged, regardless of initial particle order. While minor relaxation in particle alignment was observed, 
capillary forces alone were insufficient to drive significant structural reorganization.

Together, these results identify modes of structural response that depend upon the initial ordering of particles at the interface. The first mechanism identified occurs with
disordered particle monolayers which upon application of a magnetic field, unjam facilitating domain coarsening before rejamming once the interface area matches the 
particle cross sectional area. The second mechanism occurs due to particle reorientation to the applied field when particles are nematically ordered but not ordered in the direction
of the magnetic field.

While our simulations offer valuable insights into the tunability of bijels, they were limited to a single set of fluid and particle parameters. Future work could explore the 
effects of particle size, volume fraction, interparticle forces, and field orientation or gradients, all of which may unlock additional control over bijel structure.
Ultimately, this study establishes a foundation for stimuli-responsive bijels, showing how particle-level interactions and monolayer dynamics translate into controllable, 
application-relevant changes in material microstructure.
